\documentclass[11pt]{scrartcl}
\usepackage[sexy]{evan}

\begin{document}
\title{Philosophy of Computers and Mathematics}
\subtitle{For Future Reference}
\date{November 11, 2022}
\maketitle

\begin{abstract}
  \sffamily\small
  What ever happens next is my control

  \medskip

  --- J.S
\end{abstract}

\section{Why I want to learn math and Computer Science}
Mathematics is the way this world is expressed. To learn from this world I must adapt to it. Otherwise, I will always be stuck wondering how I can get better and never actually getting better. For example, when I was walking around on the streets at night during the time period of college applications, not asking for help when I needed it, and just wondering what my purpose in this life is, I could have been learning. To get better doesn't just mean looking at the end result, and trying to achieve it. It means enjoying everying single part of the grind.

   \textbf{What are the possible outcomes}
   
  \boldmath{$3^\ast$}  I will learn to get better at coding, at life and get the things that I want 
  
  \boldmath{$2^\ast$} Eventually I will get better at what I want, and get all the things in 3,but it will just take longer,(which is fine) 
  
  \boldmath{$1^\ast$}  Despair, always caught in a loop that I will never break out of
\footnote{This is it, be prepared for the future now}

\section{My plans for the next month before the USACO contest}
Just try and learn how to use a computer. Just thinking about computers and how they are used will be helpful. Not doing anything is not helpful. Thinking about memory and how to improve my algorithmic abilities is something that I dream to do as well. Make this dream into a reality. It can be done I just need to believe. I can learn different software as well. Like the Adobe software and Musescore and others that I discover as well. I would like to get some of my own games started as well. Life is full of possibilities I just need to go out there and take them. If something doesn't work out, keep going do not despair. 

\subsection{Always feel like you are in control}
Make sure that whatever I end up doing in my journey to understand computers, I know what I am doing. In other words, I will never be stuck being impatient or not understanding how something works. Do something rather than nothing. 
\subsection{Learning how to google}
Lots of the websites that I am looking at do not have what I want in them. They just say things but we don't know if they are actually true or not, they follow a certain pattern. I primarily use three websites, ESPN, Reddit and Wikipedia there are others but bassicaly there are only major webistes that I use and that is it.
\subsection{explicit goals that I have}
Need to state it specifically, because otherwise I only have a dream without any actionable plan to actually achieve, which I always hated with mom was saying it to me but it is true. If not now, then when?
\begin{itemize}
    \item Create a website using react native,xcode
    \item learn the inner working of my own computer, just develop a consistent working schedule, 
    \item Write papers on mathematics, on my own personal life, on my own memories
    \item Create my own cool projects of which I don't have many ideas yet, but hopefully will
    \item learn how to use sublime
    \item understand all the different errors a computer may throw at me
    \item youtube channel with adobe 
    

    
\end{itemize}
\section{Redemption}
Even though it feels hard to try and let go. I have to. This past year was one of the worst of my life. I mean it couldn't have been any worse. It wasn't because it was actually that bad, it was because all of the problems I have created for myself are of my own doing. No one else can take responsibility for that. Now I am living with the consequences. The good news is that life won't really change anymore. I am old enough now to know what things will change and what things won't. I can be the person to affect change in this world. I can and I will. 
\section{Things that I have done in this world that I am not proud of}
\begin{itemize}
    \item playing with my pencil, since 2014 in the classroom, to with my pen pal all the way to college
    \item repeating LBJ with Bohong while facetiming him
    \item Not learning algorithms and instead daydreaming for an entire year
    \item refusing to learn how to read
\end{itemize}
\section{Problem Solving}
Learn what it means to solve a problem. This means that when I am confused and am not sure what I am doing. I find a way to keep going. Even when there is uncertainity, I am not sure what I am doing, I will find a way to perservere and work through my problems. It is entirely unacceptable to give up the way I have been.
\section{Emotion}
It is also time that I start to write out the way I feel. This is all for the future. Even though I am still kind of struggling to get into the groove of things and really starting to focus (although I am getting better) I will appreciate what I am doing now in the future. The things that I do for entertainment right now will not prepare me for the future. But writing papers, learning latex and getting better at coding will. The way I feel about something will determine how I ultimately do it. For example, when I begin to feel motivated about learning how to code, I immediately start dreaming about something that, let us face it, will never happen. Just become better at understanding what the world has to offer me.
\section{Memories}
When I was walking around at Santa Clara University, I was thinking. All those times that I was walking outside at night, including that day feel like they all merge together into one. I can't really remember what actually happened on those days. And that is disappointing. Do I keep try to learn by listening to music and watching as the time ticks away? Or do I actually do something about it?
\section{Programming Languages}
This is the beginning of some notes for myself for the coming weeks as I gear up to get ready and solve for my problems and just get better at what I want to get better at.
\section{11/10}
Learning to program today was okay. I studied on the student union and played basketball from 10:30 until zoom class and then deposited my checks, studied a little bit and went to the student union where I studied for the math midterm. It was defenitely different from what I expected which was a pretty good thing. On the bus and on the way back home I listened to a lot of music and dreamed of dunking a basketball again. ( this was bad).
\subsection{C++}
\textbf{November 11th,2022} I want to create some basic programs today. Try to do a dp problem like LIS. 
\subsection{Java}
Object Oriented,
\subsection{Python}
\subsection{JavaScript}
\subsection{Pascal}
\subsection{Node.js}
\subsection{React Native}
\subsection{Dart}
\subsection{TypeScript}
\subsection{Perl}
\subsection{Ruby}
\subsection{C#}
\subsection{HTML}
Markup Language
\subsection{CSS}
\section{History of Computing}
\section{My own working Memory and Computer Memory and relationship to Algorithms}
\section{Music}
\section{software}
\section{terminal}
\section{Writing for memory}
I want to write to make sure I remember each point in my life. I also want to write and express the way that I feel exactly. This is kind. of hard. Right now, I am only writing about what I am thinking about which is frustrating. Instead of thinking more abstractly, more complicated and developing my own writing style, similar to my college applications. $$a+b^2=\int_{0}^{1} f(x)$$
\section{Memories that I remember}
\begin{itemize}
    \item 2013 Six Flags trip
    \item Great Wolf Lodge
    \item 2014 Birthday
    \item 2015 Eating at restaurant with stairs, Mom remarking about the food on the fork,walking in tennesee
    \item 2015 summer with Yuan Yuan at Yale
    \item 
\end{itemize}
\section{Purpose of Living}
There are many important reasons why I should want to continue to live. Learning about biology, what is my existence, Intelligence and IQ, how changeable is it? The history of computing and how to learn and get better at algorithms.
\section{Food I have eaten}
August 2022-November 2022-dining commons at SJSU
2021-2022 School year, School lunch, at the beginning of the year it was school lunch + lunch from home
Pandemic 2020-hot dogs and oranges while watching a move
August 2020-Going to Trader Joes on the very first day of school to buy supplies
August 2018-The very first day of school I ate two bagels from home
December 2015-Eating at a restaurant in Montana
August 2014 Eating at bear pizza
2014 Thai eating at Seattle
2014 Red Robin at Seattle
2013 Eating at restaraunts in China
\section{Movies that I have watched}
\begin{itemize}
\item Rush Hour
\item Batman Begins
\item Inception
\item Squid Game
\item Game of Thrones
\item Solo - A Star Wars Story
\item Rush Hour 1,2,3
\item Speed
\item Blind Side
\item Monsters Inc
\item Inside Out
\item Intersellar
\item Matrix
\item Black Adam
\item 2017-Modern Family on 123 movies
\item 2016-White Collar
\item 2014-2015 Agents of Shield, Some Ninjago
\item 2013 -
\item 2012- Dinasaurs, Bob the builder, Backyardigans
\item 2011 -Harry Potter and the Deathly Hallows
\item shiloh
\item Transfomers
\item The Amazing Spider Man
\item Iron Man, Iron Man 2
\item Thor
\item Captain America
\item Black Panther
\item Harry Potter
\item Star Wars
\item Mandalorian
\item Andor
\item on and off the Simpsons
\item Knives Out
\item The Star War, Skywalker Saga
\item The Office
\item Daredevil
\item Dr Strange
\item Ratatouille
\item cars
\item cars 2
\item cars 3
\item 
\end{itemize}


\end{document}

