\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{subcaption}
\usepackage[dvipsnames]{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{hyperref}
\usepackage{mathrsfs}
\usepackage{tcolorbox}
\usepackage{blindtext}
\usepackage{tcolorbox}
\usepackage{graphicx}

\usepackage[all]{xy}
\usepackage{cite}
\usepackage{url}
\usepackage{indent first}
\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
%%\usepackage[T1]{fontenc}
%%\usepackage{accanthis}
\usepackage[lf]{electrum} %% lf option gives lining figures as default; 
			  %% remove option to get oldstyle figures as default
\usepackage[T1]{fontenc}
\usepackage{hyperref}

\usepackage{tkz-fct}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{multicol}
\PassOptionsToPackage{dvipsnames,svgnames}{xcolor}
\usepackage{textcomp}


\topmargin 0.4cm
\oddsidemargin 0.5cm
 \evensidemargin 0.5cm
 \textwidth 14cm 
 \textheight 20.2 cm

 \setlength{\oddsidemargin}{0.25in}
\setlength{\evensidemargin}{0.25in}
 \setlength{\textwidth}{6in}
\setlength{\topmargin}{-0.25in}
\setlength{\textheight}{8in}

\DeclareMathOperator{\ab}{ab}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\BGL}{BGL}
\DeclareMathOperator{\Br}{Br}
\DeclareMathOperator{\card}{card}
\DeclareMathOperator{\ch}{ch}
\DeclareMathOperator{\Char}{char}
\DeclareMathOperator{\CHur}{CHur}
\DeclareMathOperator{\Cl}{Cl}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\Conf}{Conf}
\DeclareMathOperator{\disc}{disc}
\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\et}{\text{\'et}}
\DeclareMathOperator{\Fix}{Fix}
\DeclareMathOperator{\Gal}{Gal}


\begin{document}

\title{A new Paper for a new start}
\author{Jerry Sun}
%%\address{ Palo Alto, CA 94306}
%%\email{jsun5047@gmail.com}
\date{November 10th, 2022}
\maketitle

\section{My life}

Do not wait for what I can have now. I want to become the best me and therefore I need to start planning right now. Understand that whatever happens for the rest of my life is up to me starting now. It doesn't matter what happened before. If I want to affect change I can do it. I just need to believe. Try to predict what is going to happen next. Don't always be passive and think that someone is going to help you. Maybe they will, maybe some magical like Bohong will appear. But probably they won't. Enjoy what life gives you. Even if the world ends, it is time for me to start being prepared. The future waits for no one. Life waits for no one. Learning about algorithms in the moment will help me for the rest of my life. 

\section{Memories}
Here goes a document of all my life events as best that I can recall that are most notable and I would like to keep a backlog of. I can't change the past. I just have to appreciate what it gives me. Just because I don't have something that I want in the present doesn't mean that I will never have it, just dreaming about it thinking about it, for example daydreaming that I could dunk or have these weird fantasies I would ever want anyone to know about isn't going to help. Through time I will not become smarter by just existing but through my own actions. Through learning.
 \textbf{2011}:\begin{itemize} \item Niagara Falls Trip \end{itemize}
\textbf{2012}: \begin{itemize}\item Asphalt 8, \item Eating Mistyvale with Eddy, \item Vaguely remember watching the 2012 NBA finals with Don, Going to Education Connection Summer camp where RJ told me that I am scared of dying. \item Parker(I think?) telling me about Minecraft and me thinking about Lego Harry Potter Diagon Alley. \item Camping at our house
\end{itemize}
\textbf{2013}:\begin{itemize}\item  Middle finger in Miss Walker's class \item going to China in the summer \item remembering looking back out the window and seeing my cousins going back home\item Basketball at gym getting extra points because of honesty.\end{itemize}
 \textbf{2014}: \begin{itemize}\item Crying after being interrupted while reading my page in the book in Ms Martin's class. \item Michael telling me about David Yates, direction of the Harry Potter movies. \item Kyle crying after the bus driver got mad at us. The party in our backyard.\item Watching Agents of Shield with Don. \item The switch of Chinese school from Connecticut to White Plains.\end{itemize}
\textbf{2015}\begin{itemize}
\item Playing basketball in the dirty court at Dad's company \item  Bloomberg event. \item Watching Ninjago in the master bedroom at 40 Lockwood Lane. \item Watching Daredevil as well and the theme song. \item Modern family on 123 movies. \end{itemize}
 \textbf{2016} \begin{itemize}
\item Finishing WhiteCollar and feeling depressed that it was over. \item The Christmas spent with Ryan. \item the time spent at the beach and eating the sound beach pizza \item Playing with hudson \end{itemize}
 \textbf{2017}
\begin{itemize}
\item Physics Laboratory with Dad and Grace wearing Nike shirt. I remember specifically the shirt I was wearing. \item Playing basketball with Don, Mom making a bad comment and Don getting mad.(I was upset as well). \item Playing basketball with a Chinese guy with glasses. He told me to be less predictable. 
\end{itemize}
 \textbf{2018}
\begin{itemize}
\item Playing basketball at Seely and ShuShu and dad picking me up. \item Mom bringing me to the Greenville middle school and there are no spots left for me to play.\item Of course, Mathcounts Chapter Round winning the countdown round and the ride home looking at the ground. 
\item The bike rides on the trail outside our home. Eating the 6 pizzas.
\item Moving. \item The road trip I remember eating at the famous BBQ in Kansas and the night in St. Louis.\item  I also remember riding our bikes outside Zion National Park. Eating the chips in the bag was also a highlight. \item Talking to Don about TKAM. \item Going to Los Angeles in December. Mom buy me a burger near the space station. Going to the glass museum where there is a tram. 
\end{itemize}
 \textbf{2019}
\begin{itemize}
\item Geometry class, Ms Tantod telling others about my work. The AMC 10 in the geometry class. Taking two math finals at the same time. \item The teacher telling me not to use the calculator and then going to take my geometry final. \item Look at Mr Little's final message to the class at night after ARML. The bike incident in February.
\item Kenny and I in July, Learning about programming, the Don Knuth interaction and the argument at the Exploratorium. Seeing him do Musescore. Mom's work affecting her mood. Going to the Stanford Math Circle.\item  Benny I believe sneezing on me in the locker room.
\end{itemize}
\textbf{2020}
\begin{itemize}
\item The pandemic hits. All the classes become pretty easy for me to get the credit while also procrastinating on algorithms and cs. \item Watching Iron man. Watching the Office and thinking about the factorization problem. \item Talking to Bohong on Facetime.\item  Going to Google for FOOP class to Looking at the 2016 USACO and wondering about hash maps.\item  The spanish class interview with shauntel and ... Devin Shim and Timoteo. Doing basketball with timoteo. \item Talking to him after the fire drill. The person in the lunch line telling me to take a step back from him. Gal destorying me on the lap for the run we did. \item Bohong telling me to fuck the ball at the gym, On the transition with the pass, seeing the ripped asian guy. Learning about an algorithm from Kenny on hangouts


\item Qualifying for AIME and having english class immediately afterwards. Talking to MS Hexsel through Zoom. \item Doing my art final on photoshop and playing basketball at JLS> Remember that one day where the person was doing turnaround jumpers and It was dark and all the courts were full of people from the camps playing. \end{itemize}
 \textbf{2021}\begin{itemize}
\item Qualifying for AIME and having english class immediately afterwards. Talking to MS Hexsel through Zoom. \item The interaction with Mr Redfield on Zoom. What he said about my Desmos assignment. \item Doing my art final on photoshop and playing basketball at JLS Remember that one day where the person was doing turnaround jumpers and It was dark and all the courts were full of people from the camps playing.\item Thinking about devin booker and the APUSH group script project. \item Getting mad at the person with the dog. \item Thinking about what type of shoe I would want with Grace. 
\end{itemize}
 \textbf{2022}
\begin{itemize}
\item Getting back into Legos: going to the lego store in March of 2022 in SF, in April during my poetry presentation and in July after working at McDonalds and Grocery Outlet. \item The last day of class, participating in the class discussion for Literature.\item The senior picnic when the light closes down.\item Not going to Prom or my senior graduation because I left the year with all these regrets.
\item Going to the JCC with JJ.
\item My time in College: 
\item The time at the church
\item Doing chess at the library and getting to 2004
\item Doing 4 Codeforces 800 problems
\item thinking about iq, memory and what I coudl ahve done better
\item Utterly confused on codeforces, how to learn programming, how to learn algorithms. Daydreaming about things that may happen but only if I take action which I am not doing. Thinking about time, and what I have to do to. Going to the gym, then going to the bathroom while in the library. Hearing the noises from others. 
\end{itemize}

\section{Philosophy on how to work}
For me, I have always struggled with this. But now it is particulary bad. Although I think it is getting better as I am beginning to understand the root of the problem and trying to counter it. Just stop fcking daydreaming to be happy. Appreciate the algorithms. Plz do this.
\section{What is happening in the present}
Trying to think about what is happening in the present is tough but I need to start doing my algorithms, learn how to learn, and remember that the last year's obstacles will cause me a huge amount of pain in my chance to get better. Be prepared for this.
\section{Why it feels so hard to learn + 11/10 diary}
I am feeling the pain of procrastinating and not doing my best for an entire year. Right now I am struggling to learn how to use a computer. It is simply one of the most frustrating things I have ever done. I will never understand why I just couldn't start it sooner. Today, Comm was canceled, I had two midterms, did mid on both of them. Did a couple of interval runs and on the treadmill, I thought about how empty my mind is. There is simply nothing inside of my head. Learning to learn is going well though. Thinking about working memory again. Have to enjoy the grind. I spent a good hour and a half at the library from 6-7:30 doing overleaf and creating a wix, a google site and a wordpress website. Went to eat, came back and tried to learn github, saw how nice and the potential of sublime text and tried to learn some keyboard shortcuts. Downloading the game for mac is looking super hard though. Thinking about all the youtube videos I haven't watched, thinking about a different time, even when I didn't exist and didn't have these resources. But still it is so hard. 
\section{what I want in my life}
For the short term: Try to change my personality, this is something that I can do every single moment that I am alive. By January, get better at coding, come on. It is time. I have all the tools that are necessary, just go out and do it. Get a really nice santa curz bicycle. A really nice gaming pc. A nice tumi backpack. Gear. Learn what culture is, Learn what change is. Learn why what I am doing right now, just won't cut it.
\section{Thinking about algorithms}
I ams till wondering on how to learn. For example, algorithms on the internet just don't seem to be as accessible as learning math from before. Remembering the days that I would be at the library at high school printing out math competitions or at edgemont. Those were good times. Even though I had not accomplished anything, I was on a mission and I enjoyed working even though I felt sad. I had a purpose. Right now, I am not really sure if I have a purpose or not. It feels like I am just biding my time instead of really taking advantage of the moment.

\section{What is making it hard to learn to code}
Documenting my journey is the first step towards success. Right now, What I am feeling is difficult is getting the code to really work. When I am staring at a blank screen, no algorithms are coming to me even though I want to write some beautiful code. This really sucks because I feel it is the only way for me to learn at the moment, but I am just not able to do it which makes it a frustrating process.Forgetting how I was disrepected by others is the worst thing that I can do, which is what I am doing. 

\section{What does my future life look like?}
This is something that I am going to have to answer in the coming months. It is not okay for me to just keep biding my time and thinking that everything will work out. It will, but only because I change my mindset now, not because of some magical force telling me that I will change. Start change now! Try to understand that learning is the only way to get better for a person like me. (really for anyone). Without learning I am nothing.
\section{History of my interaction with computers/ technology}
The ipad in 2011. I remember specifically the mobile games I woudl play on it including Fruit Ninja, Jetpack Joyride with andy, a variant of kingdom rush, temple run, Angry Birds, Subway surfers in chinese school in 2017 and lego game in 2013. My devices include a Windows Surface Pro in 2017, a Macbook Pro from 2019. The pro was gotten at a black friday in November of 2017. I believe i got the Pro in either Late 2019 or early 2020. 
\section{Thinking about my mindest}
I have been trying to learn various algorithms for pretty much going on three years now. It just hasn't worked out. Why? Because I am learning the wrong way. For exampe. Using a computer should be something that is natural. Something that I can just do. Right now I am definitely going in the right direction but I still need to be better. Never take for granted what the computer can do for me, It is my tool for learning and getting better. 
\end{document}

